Stabilization-Free Virtual Element Methods

### 2023-02-05 reports/response.tex

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{At equation (3.4) (and continuing below) the space $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ is considered. Is this standard notation? At first I thought $\boldsymbol{x}$ was a predefined point (e.g. the centre of $T$) and the space $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ was the set of functions that could be written as a polynomial valued anti-symmetric tensor times the predefined point $\boldsymbol{x}$. However, I think what is actually meant is $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\{f:T\to\mathbb R^d: f(\boldsymbol{x})=\boldsymbol{P}_{k-2}(\boldsymbol{x})\boldsymbol{x},\quad \forall\boldsymbol{x}\in T, \boldsymbol{P}_{k-2}\in \mathbb P_{k-2}(T;\mathbb K)\}$. The authors should clarify here.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes, the notation $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ means
$$
\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\},
$$
where $\boldsymbol{\tau}\boldsymbol{x}$ is the product of the matrix $\boldsymbol{\tau}$ and the independent variable $\boldsymbol{x}\in T$. Similar notations are used in \cite{ChenHuang2021divdiv,Chen;Huang:2020Finite}.

@@

\medskip

\item \textsf{Line 149: “$(I +\boldsymbol{x}\cdot\nabla)\boldsymbol{w} = \boldsymbol{0}$, which implies $\boldsymbol{w} = \boldsymbol{0}$”. I do not see how this follows. We have that
$$(\nabla\boldsymbol{w}(\boldsymbol{x}))\boldsymbol{x}=-\boldsymbol{w}(\boldsymbol{x})\quad\forall\boldsymbol{x}\in T.
$$
It is not clear to me how the conclusion that $\boldsymbol{w} = \boldsymbol{0}$ follows. The authors
should precise their reasoning.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
The fact “$(I +\boldsymbol{x}\cdot\nabla)\boldsymbol{w} = \boldsymbol{0}$, which implies $\boldsymbol{w} = \boldsymbol{0}$” follows from \cite[(35)]{Chen;Huang:2020Finite}
%Recall (35) in \cite{Chen;Huang:2020Finite} that
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
Indeed, \eqref{eq:20230205} is a direct result of the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
$$
\boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
$$
where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
\begin{itemize}
    \item 
For virtual function $v\in V_k(K)$, apply (A.3) in \cite{ChenHuang2020ncvem} to get
\[
h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
\]
By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
\[
h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
\]
Combining the last two inequalities yields
\[
h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
\]
\item The multiplicative trace inequality is
\[
\|v\|_{0,\partial K}\lesssim h_K^{-1/2}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \quad\forall~v\in H^1(K).
\]
Since $v\in V_k(K)\subset H^1(K)$, inserting the last multiplicative trace inequality into the inequality
\[
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
\]
we get
\begin{align*}
|v|_{1,K}&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \\
&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,K}^{1/2}|v|_{1,K}^{1/2}.
\end{align*}
Then apply the Young's inequality to acquire
\[
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}.
\]
\end{itemize}

\medskip

\item \textsf{When introducing the nonconforming virtual element method in Section 4, the authors should give some references for NCVEM. In particular, I don’t think the space $V_k(K)$ is the classical NCVEM space (e.g. that defined in \cite{AyusodeDiosLipnikovManzini2016}). The authors should give reference to where this space is first introduced.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have revised the statement as follows:
Several $H^1$-nonconforming virtual elements are developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.

@@

\medskip

\item \textsf{It seems that the main novelty of this work is the construction of a space
\begin{align*}
\mathbb V_{k-1}^{\div}(K):=\{\boldsymbol{\phi}&\in L^2(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \\
& \boldsymbol{\phi}\cdot\boldsymbol{n}_F\in\mathbb P^{k-1}(F)\;\forall F\in\mathcal F(K), \boldsymbol{\phi}|_T\in\mathbb P_{k-1}(T)^d\;\forall T\in\mathcal T_K
\}
\end{align*}
and a computable $L^2$ projector $Q_{K,k-1}^{\div}$ onto $\mathbb V_{k-1}^{\div}(K)$ such that
$$
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\simeq \|\nabla v\|_{0,K} \quad\forall v\in V_k(K),
$$
where $V_k(K)$ is the non-conforming space defined at line 378 (or in Section 5 the authors consider the conforming space defined at line 544). This result is stated in Lemma 4.4 and its proof relies on the norm equivalence (3.32) and the set of uni-solvent DOFs (3.29)-(3.31). However, upon reading Section 3.2 for the first time, it is difficult to grasp what it is the authors are actually trying to achieve. Are all of the spaces, definitions and lemmas in Section 3.2 really necessary to prove Lemma 4.4? If so, the authors should state the main result of Lemma 4.4 in an earlier section, and leave much of the details of Section 3.2 and the proof of Lemma 4.4 to a later section so that readers can understand what the authors are trying to achieve.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this nice suggestion. We add the following paragraph in the beginning of Section 3.

In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
\begin{equation*}%\label{eq:Vkm1divnormequiv}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation*}
The space $\mathbb{V}_{k-1}^{\rm div}(K)$ and its $L^2$ norm equivalence will be used to prove
the norm equivalence for the virtual element space
\begin{equation*}%\label{intro:gradVknormequiv} 
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K),
\end{equation*}
where $V_k(K)$ is the nonconforming virtual element space in Section 4, and the conforming virtual element space in Section 5. Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.

@@

\medskip

\item \textsf{In Section 4, the authors design a stabilization free NCVEM for a reaction-diffusion problem, and in section 5 a stabilization free VEM. This seems an odd choice as one does not require a Poincar\'e inequality for the coercivity of the continuous bilinear form. Indeed, if
$$
a(u, v)=(\nabla u, \nabla v)_{\Omega}+\alpha (u, v)_{\Omega}
$$
with $\alpha > 0$ then it holds trivially that
$$
\|u\|_{1,\Omega}^2\leq\max(1,\alpha^{-1})a(u,u).
$$
While things mightn't be so simple at the discrete level, it would seem more
appropriate to consider a Poisson problem.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.} 
In this paper, we consider the reaction-diffusion problem with the homogeneous Dirichlet boundary condition. The Poincar\'e inequality is required for the coercivity of the bilinear form. In the continuous level, by the Poincar\'e inequality, we have the coercivity
\[
\|u\|_{1,\Omega}^2\lesssim |u|_{1,\Omega}^2\leq a(u,u)\quad \forall~u\in H_0^1(\Omega).
\]

The discrete bilinear form in this paper is defined as 
\[
a_h(u_h, v_h):=(Q_{h,k-1}^{\div}\nabla_h u_h, Q_{h,k-1}^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
\]
The discrete Poincar\'e inequality established in \cite{Brenner2003} works for the virtual element space $V_h$
\[
\|v_h\|_0\lesssim |v_h|_{1,h}\quad\forall~v_h\in V_h.
\]
This means that $|\cdot|_{1,h}$ is indeed a norm for space $V_h$. Hence, to show the coercivity of the discrete bilinear form $a_h(\cdot, \cdot)$, it suffices to prove
\begin{equation}\label{eq:11}    
|v_h|_{1,h}^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
\end{equation}
The coercivity \eqref{eq:11} is (4.19) for the nonconforming virtual element method, and~(5.8) for the conforming virtual element method.

### 2023-02-05 stabfreevem_sinum.tex
answer the second reviewer

For $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

For $d$-dimensional simplex $T$,
let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of $\boldsymbol x$ corresponding to vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$. 
For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit vector outward normal to $\partial F$ but parallel to $F$.

@@

\section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}

In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
\subsection{$H(\div)$-conforming finite elements}
For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have the decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
\end{equation}

\begin{lemma}\label{lem:skwgrad}
For $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ satisfying $(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\boldsymbol{0}$, it holds $\boldsymbol{w}=\boldsymbol{0}$.
\end{lemma}
\begin{proof}
Since
\begin{equation*}%\label{eq:20220224}  
(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\frac{1}{2}(\nabla\boldsymbol{w})\boldsymbol{x}-\frac{1}{2}(\nabla\boldsymbol{w})^{\intercal}\boldsymbol{x}=\frac{1}{2}\nabla(\boldsymbol{w}\cdot\boldsymbol{x})-\frac{1}{2}(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w},
\end{equation*}
we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which implies $\boldsymbol{w}=\boldsymbol{0}$.
\end{proof}

@@

\subsection{$H^1$-nonconforming virtual element}

Recall the $H^1$-nonconforming virtual element in \cite{ChenHuang2020ncvem,Huang2020,AyusodeDiosLipnikovManzini2016}.
The degrees of freedom are given by
\XH{
\begin{align}
\frac{1}{|F|}(v, \phi_i^F)_F, & \quad i=1,\ldots, \dim\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:vemdof2}
\end{align}
where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}

@@

\subsection{Discrete method}
Define the global nonconforming virtual element space
\begin{align*}
V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}.
\end{align*}
We have the discrete Poincar\'e inequality \XH{\cite{Brenner2003}}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
\begin{equation}\label{eq:vempoincareineqlty}
\|v_h\|_0\lesssim |v_h|_{1,h} \quad\forall~v_h\in V_h.
\end{equation}
% Introduce discrete spaces
% \begin{align*}
% \mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
% \mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
% \end{align*}
% with non-negative integer $l$.
% For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_h^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_h^{\div}\boldsymbol{\phi})|_K=Q_K^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$. For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$. For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$. And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.

@@

Recall the $H^1$-conforming virtual element in \cite{Huang2021,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
The degrees of freedom are given by
\XH{\begin{align}
v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
\end{align}
where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}
And the space of shape functions is
\begin{align*}
V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
&\qquad\qquad\qquad\qquad\qquad\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
\end{align*}
where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
It holds $\mathbb P_k(K)\subseteq V_k(K)$.
% To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by
% \begin{align}
% (\nabla\Pi_k^Kv, \nabla q)_K&=(\nabla v, \nabla q)_K\quad  \forall~q\in \mathbb P_k(K),\label{eq:projlocal1}\\
% \sum_{\delta\in\mathcal V(K)}(\Pi_k^Kv)(\delta)&=\sum_{\delta\in\mathcal V(K)}v(\delta).\label{eq:projlocal2}
% \end{align}
% It holds 
% \begin{equation}\label{eq:localprojprop1}
% \Pi_k^Kq=q \quad\forall~q\in\mathbb P_k(K).    
% \end{equation}

>>>>

For a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

For a $d$-dimensional simplex $T$,
let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of the point $\boldsymbol x$ corresponding to the vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$. 
For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit vector outward normal to $\partial F$ but parallel to $F$.

@@

\section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}
\XH{
In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
\begin{equation*}%\label{eq:Vkm1divnormequiv}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation*}
The space $\mathbb{V}_{k-1}^{\rm div}(K)$ and its $L^2$ norm equivalence will be used to prove
the norm equivalence for the virtual element space
\begin{equation*}%\label{intro:gradVknormequiv} 
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K),
\end{equation*}
where $V_k(K)$ is the nonconforming virtual element space in Section \ref{sec:stabfreencfmvem}, and the conforming virtual element space in Section \ref{sec:stabfreecfmvem}. Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.}

\subsection{$H(\div)$-conforming finite elements}
For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x},
\end{equation}
\XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
\XH{Recall (35) in \cite{Chen;Huang:2020Finite} that
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
$$
\boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
$$
where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.}

\begin{lemma}\label{lem:skwgrad}
For $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ satisfying $(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\boldsymbol{0}$, it holds $\boldsymbol{w}=\boldsymbol{0}$.
\end{lemma}
\begin{proof}
Since
\begin{equation*}%\label{eq:20220224}  
(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\frac{1}{2}(\nabla\boldsymbol{w})\boldsymbol{x}-\frac{1}{2}(\nabla\boldsymbol{w})^{\intercal}\boldsymbol{x}=\frac{1}{2}\nabla(\boldsymbol{w}\cdot\boldsymbol{x})-\frac{1}{2}(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w},
\end{equation*}
we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which \XH{together with \eqref{eq:20230205}} implies $\boldsymbol{w}=\boldsymbol{0}$.
\end{proof}

@@

\subsection{$H^1$-nonconforming virtual element}
\XH{Several $H^1$-nonconforming virtual elements are developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.}
The degrees of freedom are given by
\XH{
\begin{align}
\frac{1}{|F|}(v, \phi_i^F)_F, & \quad i=1,\ldots, \dim\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:vemdof2}
\end{align}
where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}

@@

\subsection{Discrete method}
Define the global nonconforming virtual element space
\begin{align*}
V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}.
\end{align*}
We have the discrete Poincar\'e inequality \XH{\cite{Brenner2003}}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
\begin{equation}\label{eq:vempoincareineqlty}
\|v_h\|_0\lesssim |v_h|_{1,h} \quad\forall~v_h\in V_h.
\end{equation}
\XH{Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.}
% Introduce discrete spaces
% \begin{align*}
% \mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
% \mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
% \end{align*}
% with non-negative integer $l$.
% For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_h^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_h^{\div}\boldsymbol{\phi})|_K=Q_K^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$. For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$. For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$. And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.

@@

Recall the $H^1$-conforming virtual element in \cite{Huang2021,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
The degrees of freedom are given by
\XH{\begin{align}
v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
\end{align}
where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}
And the space of shape functions is
\begin{align*}
V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
&\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\XH{\mathbb P_{k-2}^{\perp}(K)}\},
\end{align*}
where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
It holds $\mathbb P_k(K)\subseteq V_k(K)$.
% To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by
% \begin{align}
% (\nabla\Pi_k^Kv, \nabla q)_K&=(\nabla v, \nabla q)_K\quad  \forall~q\in \mathbb P_k(K),\label{eq:projlocal1}\\
% \sum_{\delta\in\mathcal V(K)}(\Pi_k^Kv)(\delta)&=\sum_{\delta\in\mathcal V(K)}v(\delta).\label{eq:projlocal2}
% \end{align}
% It holds 
% \begin{equation}\label{eq:localprojprop1}
% \Pi_k^Kq=q \quad\forall~q\in\mathbb P_k(K).    
% \end{equation}
